---
title: "Alcohol vs Seat choice"
author: "Wilhelmus Elersich"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  Judging by the median values for the three boxes, it would appear that those who consume more alcohol tend to sit in the back row.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean alcohol value for the back row is significantly higher than those of the front and middle rows, which are fairly close together. The median values behave similarly. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```  

The probability that the results gained being coincidental is slightly greater than 1 in 10000, at 0.001116 (0.0116%). Furthermore, the 95% percent confidence intervals show that the alcohol value for the back row is statistically different from the middle row and the front row. The 95% confidence interval als shows that there is no statistical difference between the front and middle rows.  

## Conclusions
Through analysis of the data, we can conclude that the back row's alcohol consumption is signifacntly higher than that of the front and middle rows, which are not statistically different from each other.

